\huge Tor's Usability for Censorship Circumvention

### 2016-04-15 pets2017-paper/pets2017-paper.tex
Fix some typos in participant quotes.
Reminder of E1, E2, E3 names.

\pquote{P8}{I have no clue what's the difference between flashpoxy, fte, etc. I need to know why the built-in ones aren't working. And why do I need a custom bridge if there are options built in?}
\pquote{P7}{Since it (obfs3) said recommended, it helped actually, and I selected it because it was chosen. I saw the custom bridges option, but I didn't know what to enter there so I went with this (obfs3).}

Participants in the advanced censorship environment were required to select a meek bridge (not the default) or to configure a custom bridge. After the first pluggable transport failed and even if the participants deduced that the source of the failed connection was a mis-configured bridge, the pluggable transport names only confused participants and caused odd behaviors. Participants chose transports at random, in order of the list starting from the default, in order of the list starting from the top, choosing familiar-sounding transports first (i.e. meek-amazon over fte), and choosing technical-sounding transports first (i.e. fte over meek-amazon).

@@

\pquote{P11}{I think you can only answer this question (does this computer need a local proxy) if you know what a local proxy is. Otherwise, you have no chance..}

@@

\subsubsection{Setup}
We simulated the same three censorship environments from 
our qualitative user study. Details of the mild, intermediate, and advanced 
censorship environments and what configurations are necessary for a 
successful connection can be found in Section~\ref{sec:environments}.

>>>>

\pquote{P8}{I have no clue what's the difference between flashproxy, fte, etc. I need to know why the built-in ones aren't working. And why do I need a custom bridge if there are options built in?}
\pquote{P7}{Since it (obfs3) said recommended, it helped actually, and I selected it because it was chosen. I saw the custom bridges option, but I didn't know what to enter there so I went with this (obfs3).}

Participants in E3, the most advanced censorship environment, were required to select a meek bridge (not the default) or to configure a custom bridge. After the first pluggable transport failed and even if the participants deduced that the source of the failed connection was a mis-configured bridge, the pluggable transport names only confused participants and caused odd behaviors. Participants chose transports at random, in order of the list starting from the default, in order of the list starting from the top, choosing familiar-sounding transports first (i.e. meek-amazon over fte), and choosing technical-sounding transports first (i.e. fte over meek-amazon).

@@

\pquote{P11}{I think you can only answer this question (does this computer need a local proxy) if you know what a local proxy is. Otherwise, you have no chance.}

@@

\subsubsection{Setup}
We simulated the same three censorship environments from 
our qualitative user study. Details of the E1, E2, and E3
censorship environments and what configurations are necessary for a 
successful connection can be found in Section~\ref{sec:environments}.
